---
title: "demo_fit_and_report"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{demo_fit_and_report}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(pcurveMix)
set.seed(1234)  # for reproducability
```

This vignette illustrates fitting the model to some observed $p$ values, performing parametric bootstrapping, and getting a complete report of the results.

First, generate some (arbitrary) random $p$ values to serve as the dataset that is to be fit.
These $p$ values are generated in accordance with the assumptions of the model.

```{r generate}
alpha_cutoff <- 1 # allow full range of p's, not selected for p<alpha significance
tails <- 2
true_mu <- 2
true_sigma <- 0.2
true_pi <- 0.3
n_ps <- 5000
sample_ps <- pcurveMix::random(n_ps, mu = true_mu, sigma = true_sigma, pi = true_pi, alpha = alpha_cutoff, tails = tails)
```

Fit the mixture model to these $p$'s and print the results as a list:

```{r}
fit_results_list <- fit_p_curve(sample_ps, alpha = alpha_cutoff, tails = tails)
print(fit_results_list)
```

Now print a nice table of parameter estimates:

```{r}
fit_tbl <- fit_to_estimates_tbl(fit_results_list)
print(fit_tbl)
```

**NEWJEFF: I still need nice reports of logLik, converged, n, ks**

Perform parametric bootstrapping using the fitted parameters:

```{r}
n_boot_samples <- 20
df <- bootstrap(n_ps, fit_results_list, n_boot_samples, alpha = alpha_cutoff, tails = tails)
boot_tbl <- bootstrap_summary(df)
print(boot_tbl)
```

Produce a wide table with the combined fitting and bootstrap results:

```{r}
combined_tbl <- merge_tables(fit_tbl, boot_tbl)
print(combined_tbl)
```

Plot histogram of the $p$ values with an overlaid line showing the predicted pdf from the fitted model.

```{r, fig.width=6}
hist(sample_ps, freq = FALSE, xlim = c(0, alpha_cutoff) )
p <- seq(0.001,0.999,0.002)
pred_pdfs <- pdf(p, mu = fit_results_list$mu, sigma = fit_results_list$sigma, pi = fit_results_list$pi,
                 alpha = alpha_cutoff, tails = tails)
lines(p, pred_pdfs, col = "red")
```

Plot a cumulative histogram of the $p$ values with an overlaid line showing the predicted cdf from the fitted model.

```{r, fig.width=6}
empirical <- ecdf(sample_ps)
plot(empirical, main = "Observed vs Predicted CDF", xlab = "p value", ylab = "CDF(p)")
pred_cdfs <- cdf(p, mu = fit_results_list$mu, sigma = fit_results_list$sigma, pi = fit_results_list$pi,
                 alpha = alpha_cutoff, tails = tails)
lines(p, pred_cdfs, col = "red")
```

