---
title: "fit_p_curve_arguments"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{fit_p_curve_arguments}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(pcurveMix)
set.seed(1234)  # for reproducability
```

This vignette gives a complete explanation of all arguments of the `fit_p_curve` function.
Then, as illustrations, it shows how to fit the model to four different sets of observed $p$ values.
The four sets differ according to whether the $p$'s come from:
- 1- or 2-tailed tests.
- all studies or studies selected for having significant results (i.e., $p \leq \alpha$)

See the `Intro_to_pcurveMix` vignette for nicer ways of displaying the fitted model and comparing its predictions to the observed $p$ values.

### `fit_p_curve` arguments

Here is the function definition:
```{r eval = FALSE}
fit_p_curve <- function(p, alpha = 1, tails = 2, alpha_sig = 0.05,
                        start = list(mu =  2, sigma = 2,    pi = 0.5),
                        lower = list(mu =  0, sigma = 1e-6, pi = 1e-6),
                        upper = list(mu = 20, sigma = 10,   pi = 1 - 1e-6))
```

- `p` is the vector of the $p$ values that are to be fit.
- `alpha` is the cutoff indicating the maximum $p$ value that might have been included in the vector `p`. This is typically either 1 if the vector includes all studies without selection for significance or else 0.05 if the vector includes only studies selected based on having significant results (i.e., $p \leq 0.05$; e.g., published studies).
- `tails` must be 1 or 2 to indicate whether the $p$ values reflect 1- or 2-tailed tests of the studies' null hypotheses.
- `alpha_sig` After the $p$-curve model is fit, its parameters can be used to estimate the average power of studies in which a true effect is present (i.e., H1 is true). That power depends on the $\alpha$ level used as the significance cutoff for which you would like power computed, which is specified by this argument. With the default value of `alpha_sig = 0.05`, for example, power will be estimated as the probability of obtaining $p \leq 0.05$ in a study with a true effect.
- `start` is a list of starting parameter values that is passed to R's `optim` numerical search function. When analyzing a real dataset of $p$'s, it is a good idea to run `fit_p_curve` several times from different starting point to make sure that it converges to the same parameter estimates in all cases (i.e., there are no local minimum problems).
- `lower` and `upper` are lists of the minimum and maximum allowable values of the three parameters that are passed to `optim`.

### First, generate some (arbitrary) random $p$ values to serve as the dataset that is to be fit:

```{r generate, fig.width=6}
# A crude method of generating p values with especially many significant ones.
ps_h0 <- runif(500)
ps_h1 <- runif(500)^4
ps <- c(ps_h0, ps_h1)
hist(ps)
```

### Fit the mixture model to these $p$'s:

The default arguments of `fit_p_curve` specify that these are 2-tailed $p$'s in the full 0-1 range.

```{r}
fit_results_2tailed <- fit_p_curve(ps) 
estimates_tbl <- fit_to_estimates_tbl(fit_results_2tailed)
knitr::kable(estimates_tbl)
```

### Alternatively, fit the same $p$'s assuming that they come from 1-tailed tests:

...still using the default 0-1 range of $p$'s.

```{r}
fit_results_1tailed <- fit_p_curve(ps, tails = 1)
estimates_tbl <- fit_to_estimates_tbl(fit_results_1tailed)
knitr::kable(estimates_tbl)
```

### Select out the significant $p$'s and refit the model using just those.

The `alpha` parameter is used to indicate to the fitting function that these $p$ values
were pre-selected to be significant.

```{r}
alpha <- 0.05
ps_sig <- ps[ps < alpha]

fit_sig_results_2tailed <- fit_p_curve(ps_sig, alpha = alpha) # assumes 2-tailed p's in 0-alpha range
estimates_tbl <- fit_to_estimates_tbl(fit_results_2tailed)
knitr::kable(estimates_tbl)

fit_sig_results_1tailed <- fit_p_curve(ps_sig, alpha = alpha, tails = 1) # or assuming 1-tailed
estimates_tbl <- fit_to_estimates_tbl(fit_results_1tailed)
knitr::kable(estimates_tbl)
```

