---
title: "Intro"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Intro}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  markdown: 
    wrap: sentence
---

```{=html}
<style>
.title {
  display: none;
}
</style>
```

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction to `pcurveMix`

This introductory vignette illustrates two options for the simplest and most common use case of fitting the mixture model of Ulrich and Miller (in preparation) to a set of observed $p$ values obtained from statistical tests.
Specifically, this is the use case in which:

-   you have a set of observed $p$ values from a given research area.

-   you would like to fit the mixture model to those $p$ values in order to get estimates of the three model parameters describing the research area from which those $p$ values were obtained:

    -   `pi` or $\pi$, the proportion of studies in which real effects are present (i.e., H1 is true).
    -   `mu` or $\mu$, the mean of those studies' effect sizes.
    -   `sigma` or $\sigma$, the standard deviation of those studies' effect sizes.

The fitting process provides estimates, standard errors, and confidence intervals for those model parameters, as well as plots of observed and fitted frequency distributions and cumulative frequency distributions of $p$ values.

# Option 1: Fitting with the shiny app

The simplest way to fit the model is by using the shiny app that comes with the package.
Use the following RStudio command to start the app:

```{r, eval = FALSE}
run_shiny_app()
```

## Setup for fitting

Once the app opens, use the setup panel to set these arguments of the fitting process:

1.  Choose the CSV file with the $p$ values that are to be analyzed.
    This file should contain a column named "p" with the $p$ values from the different studies.
    Other columns, if any, are ignored.
    For this demo run, just check the checkbox to use the `sample_ps.csv` file of $p$ values supplied with the package.
    These are some (arbitrary) random $p$ values that were generated previously (in accordance with the assumptions of the model).

2.  Indicate whether the $p$ values in the file come from 1- or 2-tailed testing (because the computations are slightly different for these two cases).
    The `sample_ps.csv` has 2-tailed $p$'s (the default).

3.  Indicate the upper $p$ cutoff for inclusion in the file (a.k.a. `alpha` or $\alpha$).
    This cutoff is the largest $p$ value that could possibly have been included in the `sample_ps` vector.
    The cutoff of 1, shown here, indicates that $p$ values could come from any study, significant or not.
    Alternatively, a cutoff of 0.05 would be appropriate if the $p$'s all came from published studies, given the common editorial practice of requiring $p \leq 0.05$ for publication.
    If the file contains any $p$ values larger than the cutoff, these are discarded prior to fitting.
    For this demo run, use the default value of 1.

4.  Indicate an alpha level for power computations (a.k.a. `alpha_sig`).
    The fitted values of $\mu$ and $\sigma$ can be used to compute the average power of studies in which a true effect is present (i.e., H1 is true), but only in relation to the $\alpha$ level used as the significance cutoff, which is specified by this argument.
    With the default value of `alpha_sig = 0.05`, for example, power will be estimated as the probability of obtaining $p \leq 0.05$ in a study with a true effect.
    Use the default of 0.05 for this demo run.

5.  Indicate the number of samples for the parametric bootstrap analysis.
    This is reasonably fast and we recommend using at least 2000 samples for any "real" analysis.
    Of course you can reduce it to 100 or 200 for quick testing, or even to 0 to skip bootstrapping entirely.
    For this demo run, use a value of 100.

6.  Optionally, you can adjust the starting values for $\mu$, $\sigma$, and $\pi$ that are given to optim. We have not found much effect of changing these values but there could be an effect with some datasets.

7.  There are also a few other rather technical variables that can be adjusted using the `set_globals` function (see that function's documentation). Use the following command sequence to change the values of these variables:

```{r eval = FALSE}
library(pcurveMix)
set_globals(edge_p = 1e-13) # Set any values here
run_shiny_app()
```

After you have set the above arguments, click the `Fit model` button and the results will appear as shown next.

There is also a `Download results` button that can be used after the model has been fit.
This produces a `zip` file with the fitting results.
The `zip` includes a `docx` file with the fitting results shown by the shiny app, and it also includes `CSV` files showing the model's predicted PDF and CDF values with the estimated parameters (in case you would like to make your own plots).

## Maximum-likelihood fitting results

```{r,  eval = TRUE, echo = FALSE}
p_file_name <- "sample_ps.csv"
package_path <- system.file(package = "pcurveMix")
file_name <- paste0(package_path,"/extdata/",p_file_name)
```

```{r library_and_read_ps, eval = TRUE, echo = FALSE, message = FALSE, warning = FALSE}
library(pcurveMix)

# file_name <- "Set your file_name here"

df <- read.csv(file_name)
sample_ps <- df$p
n_ps <- length(sample_ps)
```

```{r fit_model, eval = TRUE, echo = FALSE}
alpha_cutoff <- 1 # allow full range of p's, not selected for p<alpha significance
tails <- 2
fit_results_list <- fit_p_curve(sample_ps, alpha = alpha_cutoff, tails = tails)
```

### Fitting summary table

The first table is a summary of the fitting conditions and overall results.

```{r print_descriptors, echo = FALSE}
# print(fit_results_list)  # Ugly list format printing; better in next 2 tables.
descriptor_tbl <- fit_to_descriptor_tbl(fit_results_list, file_name = p_file_name)
knitr::kable(descriptor_tbl)
```

The first part of this table gives information about the fitting options `alpha`, `tails`, and `alpha_sig` as specified in the setup panel. It also shows the starting parameter values passed to the `optim` function.

The second part of the table gives information about the dataset of $p$'s to which the model has been fit, including the number of $p$ values in the dataset as well as the minimum and maximum of these $p$ values.
Notations are also included here if any $p$ values were excluded for being less than zero or greater than the `alpha` cutoff.
In addition, $p$ values of 0 cause numerical errors in the fitting computations, so it is noted if any of these have been replaced with a smaller value.

The third part of the table gives information about the overall results of the model fit:

-   Whether or not the `optim` function reported convergence on a final set of parameter estimates.
-   The overall log likelihood of the $p$'s dataset under the model with the estimated parameter values.
-   The value of the Kolmogorov-Smirnov Dmax test statistic comparing the observed and model-predicted CDFs of $p$ values.
-   The $p$ value of the Kolmogorov-Smirnov test, where the H0 is that the observed $p$ values came from the model-predicted distribution of $p$'s.

### Parameter estimates table

The next table shows the estimates for the model parameters $\mu$, $\sigma$, and $\pi$.
Here, for example, it is estimated that the probability of a real effect (H1 true) in this research area is 0.304 and that---when a real effect is present---the size of that effect (in Z-score terms) comes from a normal distribution with a mean of 1.927 and a standard deviation of 1.953.

Also shown is the estimated power---that is, the probability of rejecting H0 when H1 is true.
(This is essentially an average power computed across the distribution of possible true effect sizes with the estimated $\mu$ and $\sigma$).
There is no standard error or confidence interval for power because it is derived from the others.

```{r print_parameter_estimates, echo = FALSE}
estimates_tbl <- fit_to_estimates_tbl(fit_results_list)
knitr::kable(estimates_tbl)
```

#### Additional bootstrap analysis table

The bootstrap analysis provides bootstrap means, standard errors, and confidence intervals for the parameters.
These are computed across the indicated number of bootstrap samples, where for each sample the program:

-   generates a random sample of $p$ values from the mixture model with the estimated values of the parameters $\mu$, $\sigma$, and $\pi$.
-   fits the model to this new sample of $p$'s to obtain new estimates of $\mu$, $\sigma$, and $\pi$, as well as to compute a new estimate of power given the specified `alpha_sig` criterion.

```{r bootstrap_analysis, echo = FALSE, comment = ""}
n_boot_samples <- 100  # Smaller number for demo, but 2000 recommended minimum for real analyses; more is better
df <- bootstrap(n_ps, fit_results_list, n_boot_samples,
                alpha = alpha_cutoff, tails = tails, show_progress_bar = FALSE)
boot_list <- make_bootstrap_summary_list(df, estimates_tbl)
cat("* n bootstrap samples =",n_boot_samples,"\n")
cat("* percent converged OK =",round(boot_list$pct_converged,2),"\n")
knitr::kable(boot_list$boot_tbl)
```

The outputs show the percentage of bootstrap samples for which the fitting process converged with legal parameter values (e.g., $0\leq\pi\leq1$) and the means, standard errors, and confidence intervals of the parameter estimates across the different bootstrap samples.

```{r BC_est_explanation, echo = FALSE}
mu_row <- 1 # estimates_tbl$parameter == "estimate"
mu_est <- estimates_tbl$estimate[mu_row]
boot_mean_mu <- boot_list$boot_tbl$Boot_Mean[mu_row]
bias <- boot_mean_mu - mu_est
bc_est <- 2*mu_est - boot_mean_mu
```

It also includes the `BC_est` column to show *bias-corrected* parameter estimates.
These are the original parameter estimates that are *corrected for* any bias that is suggested by the mean of the bootstrap sample estimates.

Here is an illustration of the bias correction for the $\mu$ parameter in the current example.
As shown in the "Parameter estimates" table, the original estimate of $\mu$ was `r mu_est`.
This value was then used as the true $\mu$ for all of the parametric bootstrap samples.
Therefore, if there were no bias, the "Boot_Mean" would also be (very close to) `r mu_est`.
But the actual "Boot_Mean" for $\mu$ was `r boot_mean_mu`, suggesting that there is an estimation bias of

<center>`r boot_mean_mu` - `r mu_est` = `r bias`.</center>

The `BC_est` value is thus computed as

<center>`r mu_est` - `r bias` = `r bc_est`</center>

to correct for this bias.

### PDF and CDF plots

The next output is a (density-scaled) histogram of the sample $p$ values superimposed over the predicted density at each $p$ from the fitted model:

```{r, fig.width=6, echo = FALSE}
quick_pdf_plot(fit_results_list)
```

The final plot shows the empirical CDF of the $p$ values and the predicted CDF from the fitted model:

```{r, fig.width=6, echo = FALSE}
quick_cdf_plot(fit_results_list)
```

## Option 2: Fitting with an R script

For automation or finer-grained control over the fitting process, you can fit the model with a simple `R` script instead of the shiny app, as follows.

### Load package and read example dataset of $p$ values

Typically, users would have their own datasets of $p$ values to which the model should be fit.

```{r ref.label = "library_and_read_ps", eval = FALSE, echo = TRUE}
```

### Fit the model to the example dataset

Fit the mixture model to these $p$'s with the default vallues of `alpha` and `tails`.
The `fit_p_curve` function has a number of other optional arguments (for details, see the `fit_p_curve_details` vignette).

```{r ref.label = "fit_model", eval = FALSE, echo = TRUE}
```

Note that the `fit_p_curve` output is called `fit_results_list`; this list is used as input to several subsequent functions.

### Print a table summarizing the model fit:

This prints the table summarizing the fitting conditions and overall results.

```{r ref.label = "print_descriptors", eval = FALSE, echo = TRUE}
```

### Print a table summarizing the parameter estimates:

```{r ref.label = "print_parameter_estimates", eval = FALSE, echo = TRUE}
```

### Perform parametric bootstrapping using the fitted parameters:

```{r ref.label = "bootstrap_analysis", eval = FALSE, echo = TRUE}
```

### Make PDF and CDF plots

This command makes a (density-scaled) histogram of the sample $p$ values and superimposes over it the predicted density at each $p$ from the fitted model:

```{r, fig.width=6, eval = FALSE}
quick_pdf_plot(sample_ps, fit_results_list)
```

This command plots the empirical CDF of the $p$ values and the predicted CDF from the fitted model:

```{r, fig.width=6, eval = FALSE}
quick_cdf_plot(sample_ps, fit_results_list)
```

Finally, here are alternative methods of making the PDF and CDF plots that give you more control over the output formats:

```{r, eval = FALSE}
library(ggplot2)

# Define a sequence of p values at which to get predicted PDFs and CDFs:
p_seq <- seq(0.001, alpha_cutoff, 0.002)

# Compute & plot predicted PDFs:
pred_pdfs <- pdf(p_seq, mu = fit_results_list$mu,
                 sigma = fit_results_list$sigma,
                 pi = fit_results_list$pi,
                 alpha = alpha_cutoff, tails = tails)
pdf_plot <- ggplot() +
 geom_histogram(aes(x = sample_ps, y = after_stat(density)), # empirical
                binwidth = 0.02) +
 geom_line(aes(x = p_seq, y = pred_pdfs), color = "red")  # predicted
print(pdf_plot)

# Compute & plot predicted CDFs:
pred_cdfs <- cdf(p_seq, mu = fit_results_list$mu,
                 sigma = fit_results_list$sigma,
                 pi = fit_results_list$pi,
                 alpha = alpha_cutoff, tails = tails)
cdf_df <- data.frame(x = sample_ps)
cdf_plot <- ggplot() +
 stat_ecdf(data = cdf_df, aes(x = x), geom = "step") +  # empirical
 geom_line(aes(x = p_seq, y = pred_cdfs), color = "red") +  # predicted
 labs(title = "Observed (black) vs predicted (red) CDFs",
      x = "p value",
      y = "cumulative proportion")
print(cdf_plot)
```
