---
title: "pcurveMix Fit Report"
date: "`r format(Sys.time(), '%Y_%m_%d_%H_%M_%S')`"
output:
  word_document:
    reference_docx: pcurveMix_style.docx
params:
  p_filename: NA
  tails : NA
  descriptor_tbl: NA
  estimates_tbl: NA
  estimates_notes: NA
  pdf_plot: NA
  cdf_plot: NA
  n_jack_samples: NA
  jack_tbl: NA
  jack_notes: NA
  n_boot_samples: NA
  boot_tbl: NA
  boot_notes: NA
  np_n_boot_samples: NA
  np_boot_tbl: NA
  np_boot_notes: NA
  profile_analysis: NA
  profile_tbl: NA
  profile_mu_plot: NA
  profile_sigma_plot: NA
  profile_pi_plot: NA
  profile_power_plot: NA
  profile_folded_normal_mu_plot: NA
  profile_folded_normal_sigma_plot: NA
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.width = 6, fig.height = 4)
# Fitting observed $p$ values with the mixture model of Ulrich & Miller (2026, submitted).
```

# Maximum-likelihood fitting summary

## Fitting parameters and summary results

```{r print_fitting_parameters, echo=FALSE, results='asis'}
print(knitr::kable(params$descriptor_tbl))
```

## Parameter estimates

```{r print_parameter_estimates, echo=FALSE, results='asis'}
print(knitr::kable(params$estimates_tbl))
```
```{r echo = FALSE}
bullet_list <- paste("-", params$estimates_notes, collapse = "\n")  # paste adds space after "-"
knitr::asis_output(bullet_list)
```

## Observed/predicted PDFs:

Note: The X/Y pairs for the following plots of predicted PDF, predicted CDF, and (if requested) likelihood profiles were saved in `*.csv` files within the downloaded zip file.

```{r plot pdf, echo=FALSE}
plot(params$pdf_plot)
```

## Observed/predicted CDFs:

```{r plot cdf, echo=FALSE}
plot(params$cdf_plot)
```


```{asis, echo = params$n_jack_samples > 0}
## Jackknifing analysis
```
```{r print_jack_tbl, echo=FALSE, results='asis', eval = params$n_jack_samples > 0}
print(knitr::kable(params$jack_tbl))
```
```{r echo = FALSE}
bullet_list <- paste("-", params$jack_notes, collapse = "\n")  # paste adds space after "-"
knitr::asis_output(bullet_list)
```


```{asis, echo = params$n_boot_samples > 0}
## Parametric bootstrapping analysis
```
```{r print_boot_tbl, echo=FALSE, results='asis', eval = params$n_boot_samples > 0}
print(knitr::kable(params$boot_tbl))
```
```{r echo = FALSE}
bullet_list <- paste("-", params$boot_notes, collapse = "\n")  # paste adds space after "-"
knitr::asis_output(bullet_list)
```


```{asis, echo = params$np_n_boot_samples > 0}
## Nonparametric bootstrapping analysis
```

```{r print_np_boot_tbl, echo=FALSE, results='asis', eval = params$np_n_boot_samples > 0}
print(knitr::kable(params$np_boot_tbl))
```
```{r echo = FALSE}
bullet_list <- paste("-", params$np_boot_notes, collapse = "\n")  # paste adds space after "-"
knitr::asis_output(bullet_list)
```



```{asis, echo = params$profile_analysis > 0}
## Profile analysis
```

```{r profile_tbl, echo=FALSE, results='asis', eval = params$profile_analysis > 0}
print(knitr::kable(params$profile_tbl))
```

```{r profile_plots, echo=FALSE, eval = params$profile_analysis > 0}
plot(params$profile_mu_plot)
plot(params$profile_sigma_plot)
plot(params$profile_pi_plot)
plot(params$profile_power_plot)
if (params$tails == 2) {
  plot(params$profile_folded_normal_mu_plot)
  plot(params$profile_folded_normal_sigma_plot)
}
```

## Additional files

In addition to this document, the downloaded `Zip` file also contains `csv` files with the x/y coordinates for the plots shown in this document so that you can conveniently remake the plots.
